Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
rewrite data & code availability

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
Raw data, analysis scripts to generate the results from the raw data as well as
the results are available from *TBA*, and accessible as Datalad
(RRID:SCR_003931) datasets.

>>>>

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
The fMRI and annotation data, analysis scripts to generate the results as well
as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
accessible as Datalad (RRID:SCR_003931) datasets.
